\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-27 paper.tex
Caption of python code snippet

\end{pythoncode}
    \caption{Example of a simple \uwds Python client named {\tt walls\_filter}:
    the client connects to the \uwds network, efficiently accesses the world
    {\tt example\_in}, filter out some objects, and publish the remaining
    objects in the world {\tt example\_out}.} \label{lst|pythonapi}
\end{listing}

>>>>

\end{pythoncode}
    \caption{Example of a simple \uwds filter, written in Python, and named {\tt
    walls\_filter}: the client connects to the \uwds network, walkthrough the
    scene graph of world {\tt example\_in}, filter out some objects, and publish
    the remaining objects in the world {\tt example\_out}.}

    \label{lst|pythonapi}
\end{listing}
